---
title: "Data Exploration"
author: "Owen Wurst"
date: "Started January 3rd, 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The first step of this project is to read in the yahoo finance data and transform it into data that I know how to run ml algorithms on, as well as do some exploratory data analysis and visualization so I have some preliminary knowledge to inspire some model formation.

## Libaries and Imports:
```{r, imports}
library(tidyverse)
library(gridExtra)
library(grid)

source("Data_Prep_Functions.r")
source("Data_Viz_Functions.r")
```

# Data Preparation:
## Reading in Data:
I will start by reading the csv files for all of the data. I will add a column for ticker and industry to each df.
```{r, create_df_list}
# Tech
apple <- read("Original_Datasets/YahooFinance/AAPL.csv")
appl_df <- prep_df_post_csv_read(apple, "APPL", "Tech")

nvidia <- read("Original_Datasets/YahooFinance/NVDA.csv")
nvda_df <- prep_df_post_csv_read(nvidia, "NVDA", "Tech")

meta <- read(  "Original_Datasets/YahooFinance/META.csv")
meta_df <- prep_df_post_csv_read(meta, "META", "Tech")

# Pharma
jnj <- read("Original_Datasets/YahooFinance/JNJ.csv")
jnj_df <- prep_df_post_csv_read(jnj, "JNJ", "Pharma")

moderna <- read("Original_Datasets/YahooFinance/MRNA.csv")
mrna_df <- prep_df_post_csv_read(moderna, "MRNA", "Pharma")

abbvie <- read("Original_Datasets/YahooFinance/ABBV.csv")
abbv_df <- prep_df_post_csv_read(abbvie, "ABBV", "Pharma")

# Banking
jpmorg <- read("Original_Datasets/YahooFinance/JPM.csv")
jpm_df <- prep_df_post_csv_read(jpmorg, "JPM", "Banking")

mandt <- read("Original_Datasets/YahooFinance/MTB.csv")
mtb_df <- prep_df_post_csv_read(mandt, "MTB", "Banking")

pnc <- read("Original_Datasets/YahooFinance/PNC.csv")
pnc_df <- prep_df_post_csv_read(pnc, "PNC", "Banking")

# Retail
target <- read("Original_Datasets/YahooFinance/TGT.csv")
tgt_df <- prep_df_post_csv_read(target, "TGT", "Retail")

wmt <- read("Original_Datasets/YahooFinance/WMT.csv")
wmt_df <- prep_df_post_csv_read(wmt, "WMT", "Retail")

costco <- read("Original_Datasets/YahooFinance/COST.csv")
cost_df <- prep_df_post_csv_read(costco, "COST", "Retail")

# Add to List
stock_df_list <- list(
  appl_df, nvda_df, meta_df,
  jnj_df, mrna_df, abbv_df,
  jpm_df, mtb_df, pnc_df,
  tgt_df, wmt_df, cost_df
)
```

After that, we have a list of 12 dataframes that look like this.
```{r, show_target}
head(tgt_df)
```

## Data Visualization:
I will now take a look at some of the data I have read in to start to visualize some of  the trends.

### Stock Price Changes by Industry:

#### Tech Stocks:
```{r, tech_stock_prices}
df_list <- list(apple, meta, nvidia)
names_list <- list("Apple", "Meta", "Nvidia")
industry <- "Tech"

create_industry_graphs(df_list, names_list, industry, "Line_Graph")
```

```{r, adjusted_tech_stock_prices}
df_list <- list(apple, meta, nvidia)
names_list <- list("Apple", "Meta", "Nvidia")
industry <- "Tech"

create_industry_graphs(df_list, names_list, industry, "Line_Graph", adjusted = TRUE)
```

```{r, tech_stock_prices_hist}
df_list <- list(appl_df, meta_df, nvda_df)
names_list <- list("Apple", "Meta", "Nvidia")
industry <- "Tech"

create_industry_graphs(df_list, names_list, industry, "Histogram")
```

```{r, adjusted_tech_stock_prices_hist}
df_list <- list(appl_df, meta_df, nvda_df)
names_list <- list("Apple", "Meta", "Nvidia")
industry <- "Tech"

create_industry_graphs(df_list, names_list, industry, "Histogram", adjusted = TRUE)
```

#### Banking Stocks
```{r, banking_stock_prices}
df_list <- list(jpmorg, mandt, pnc)
names_list <- list("JP Morgan", "M&T Bank", "PNC")
industry <- "Banking"

create_industry_graphs(df_list, names_list, industry, "Line_Graph")
```

```{r, adjusted_banking_stock_prices}
df_list <- list(jpmorg, mandt, pnc)
names_list <- list("JP Morgan", "M&T Bank", "PNC")
industry <- "Banking"

create_industry_graphs(df_list, names_list, industry, "Line_Graph", adjusted = TRUE)
```

```{r, banking_stock_prices_hist}
df_list <- list(jpm_df, mtb_df, pnc_df)
names_list <- list("JP Morgan", "M&T Bank", "PNC")
industry <- "Banking"

create_industry_graphs(df_list, names_list, industry, "Histogram")
```

```{r, adjusted_banking_stock_prices_hist}
df_list <- list(jpm_df, mtb_df, pnc_df)
names_list <- list("JP Morgan", "M&T Bank", "PNC")
industry <- "Banking"

create_industry_graphs(df_list, names_list, industry, "Histogram",adjusted = TRUE)
```

#### Pharmaceutical Stocks
```{r, pharma_stock_prices}
df_list <- list(jnj, moderna, abbvie)
names_list <- list("Johnson and Johnson", "Moderna", "AbbVie")
industry <- "Pharma"

create_industry_graphs(df_list, names_list, industry, "Line_Graph")
```

```{r, adjusted_pharma_stock_prices}
df_list <- list(jnj, moderna, abbvie)
names_list <- list("Johnson and Johnson", "Moderna", "AbbVie")
industry <- "Pharma"

create_industry_graphs(df_list, names_list, industry, "Line_Graph", adjusted = TRUE)
```

```{r, tech_stock_price_changes_hist}
df_list <- list(jnj_df, mrna_df, abbv_df)
names_list <- list("Johnson and Johnson", "Moderna", "AbbVie")
industry <- "Pharma"

create_industry_graphs(df_list, names_list, industry, "Histogram")
```

```{r, adjusted_tech_stock_price_changes_hist}
df_list <- list(jnj_df, mrna_df, abbv_df)
names_list <- list("Johnson and Johnson", "Moderna", "AbbVie")
industry <- "Pharma"

create_industry_graphs(df_list, names_list, industry, "Histogram", adjusted = TRUE)
```

#### Retail Stocks
```{r, retail_stock_prices}
df_list <- list(wmt, target, costco)
names_list <- list("Walmart", "Target", "Costco")
industry <- "Retail"

create_industry_graphs(df_list, names_list, industry, "Line_Graph")
```

```{r, adjusted_retail_stock_prices}
df_list <- list(wmt, target, costco)
names_list <- list("Walmart", "Target", "Costco")
industry <- "Retail"

create_industry_graphs(df_list, names_list, industry, "Line_Graph", adjusted = TRUE)
```

```{r, retail_stock_price_changes_hist}
df_list <- list(wmt_df, tgt_df, cost_df)
names_list <- list("Walmart", "Target", "Costco")
industry <- "Retail"

create_industry_graphs(df_list, names_list, industry, "Histogram")
```

```{r, adjusted_retail_stock_price_changes_hist}
df_list <- list(wmt_df, tgt_df, cost_df)
names_list <- list("Walmart", "Target", "Costco")
industry <- "Retail"

create_industry_graphs(df_list, names_list, industry, "Histogram", adjusted = TRUE)
```

## Data Transformation:
I am now going to create dataframes where each line represents an 8 month period of changes for every line that I can in these dateframes. I will save this as a csv to be used in the actual training dataframe
```{r, create_learning_df_8}
full_learning_df_8_months <- make_full_learning_df(stock_df_list, 8)
write.csv(
  full_learning_df_8_months,
  file = "PriceChangeByPrevious8Months_Training.csv",
  row.names = FALSE
)
```

6 Month DF
```{r, create_learning_df_6}
full_learning_df_6_months <- make_full_learning_df(stock_df_list, 6)
write.csv(
  full_learning_df_6_months,
  file = "PriceChangeByPrevious6Months_Training.csv",
  row.names = FALSE
)
```

12 Month DF:
```{r, create_learning_df_12}
full_learning_df_12_months <- make_full_learning_df(stock_df_list, 12)
write.csv(
  full_learning_df_12_months,
  file = "PriceChangeByPrevious12Months_Training.csv",
  row.names = FALSE
)
```

4 Month DF:
```{r, create_learning_df_4}
full_learning_df_4_months <- make_full_learning_df(stock_df_list, 4)
write.csv(
  full_learning_df_4_months,
  file = "PriceChangeByPrevious4Months_Training.csv",
  row.names = FALSE
)
```

10 Month DF:
```{r, create_learning_df_10}
full_learning_df_10_months <- make_full_learning_df(stock_df_list, 10)
write.csv(
  full_learning_df_10_months,
  file = "PriceChangeByPrevious10Months_Training.csv",
  row.names = FALSE
)
```
